Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-07-17 Latex/journal_v1/V5/pr.tex
add figure

 %\pdfoutput=1
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\setlength{\columnsep}{11mm}
\begin{document}

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,k)}} \ \\

@@

In Fig. \ref{fig:1} the aggregated throughput is demonstrated versus different number of UEs in each service for these three methods. Here we assume that services have the same priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.

@@

    \includegraphics[scale = 0.45]{rate_ue1.eps}

@@

\section{Conclusion}\label{conc}
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

>>>>

 %\pdfoutput=1
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfigure}
\usepackage{graphicx}
\usepackage{blindtext}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\diag}{\mathop{\mathrm{diag}}}
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage[margin=0.7in]{geometry}
\usepackage[export]{adjustbox}
\setlength{\columnsep}{11mm}
\begin{document}

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{E}, \boldsymbol{M}, \boldsymbol{G} }   \quad &  \sum_{s=1}^{S}\sum_{i=1}^{U_s}\delta_s \bar{\mathcal{R}}_{u_{(s,i)}} \ \\

@@

In Fig. \ref{fig:1} the aggregate throughput is demonstrated versus different number of UEs in each service for these three methods. Here we assume that services have the same priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.

@@

    \includegraphics[scale = 0.4]{rate_ue1.eps}

@@

Assume we have two services of URLLC and mMTC. In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{mmtcurllc.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
  \label{fig:2}
\end{figure}
In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{sumRatePri.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
  \label{fig:3}
\end{figure}

\section{Conclusion}\label{conc}
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}
